\Title

### 2023-06-01 Grimaldi-etal-BiolCybernetics.tex
Update Grimaldi-etal-BiolCybernetics.tex

In this paper, we aim to test whether the HD-SNN model is capable of efficiently learning a motion detection task, which is defined by a realistic event-based data stream. This type of signal is typically captured by a Dynamic Vision Sensor (DVS) and is inspired by the signal that is sent from the retinal ganglion cells through the optic nerve. The events are binary in nature and should be sufficient to perform the task of motion detection in a fast and efficient manner. Here we will first describe the task definition and then the HD-SNN model we use for motion inference and how we train it. 

>>>>

In this paper, we test whether the HD-SNN model is able to efficiently learn a motion detection task defined by a realistic event-based data stream. This type of signal is commonly captured by a Dynamic Vision Sensor (DVS) and is inspired by the signal sent from the retinal ganglion cells through the optic nerve to the visual cortex. The events are binary in nature and should be sufficient to perform the motion detection task in a fast and efficient manner. Here we first describe the task definition and then the HD-SNN model we use for motion inference and how we train it.
